---
title: "Practice"
author: "Lesly"
date: "2024-10-13"
output: html_document
---

## Create the data frame by creating each column

```{r}
library(tidyr)
library(dplyr)
plants<-c('plant 1', 'plant 2', 'plant 3', 'plant 4', 'plant 5')
start_height<-c(4.0, 5.0, 3.0, 6.0, 7.0)
end_height<-c(9.0, 6.0, 5.0, 4.0, 7.0)
```



## Create a table with the data frame
```{r}
experiment<-data.frame(plant = plants, start_experiment = start_height, end_experiment = end_height)
print(experiment)
```



## Reformat the data frame
### Make the time just one column by using pivot_longer
```{r}
experiment_ref <- experiment %>%
         pivot_longer(cols = starts_with("start_experiment"):starts_with("end_experiment"), names_to = "time", values_to = "height")
experiment_ref
```



## Change the time measurement column in a factor of 2 levels
```{r}
experiment_ref$time<-factor(experiment_ref$time, levels = c("start_experiment", "end_experiment"))
print(experiment_ref)
```



## The second element of this list will be another list called "growth", in which three elements are stored: [1] a character vector extracting the row names of the previously created table ; [2] a numeric vector (double) indicating the change in height of each plant (can be positive or negative, but will be calculated as a percentage of the initial height), and [3] a combination of these two elements in a table with two columns: plants and growth

### To calculate percentage growth
```{r}
growth_percentage<-(experiment$end_experiment - experiment$start_experiment) / experiment$start_experiment * 100
```



### Then create the "growth" list
```{r}
growth<-list(rownames = rownames(experiment), percentage_change = growth_percentage, summary.table = data.frame(plant = plants, growth = growth_percentage))
print(growth)
```



## Write a message about the growth status of these plants
```{r}
growth_message<-"Three out of five plants show positive growth changes"
```



## Generate a final list
```{r}
my_experiment<-list(experiment = experiment_ref, growth = growth, message = growth_message)
print(my_experiment)
```

